\section{Reproducibility}\label{sec:repro}

All empirical results in this report are reproducible from the
public repository \texttt{roastercode/beamfs} at tag
\texttt{v0.4.0-palier4-validated}, commit
\texttt{7c30934}~\cite{beamfs-impl}, GPG-signed by key
\texttt{319A8EAA89C7538AA9550E8BC35EE212519E4857}.

\paragraph{Build environment.}
The build environment is a Yocto image
(\texttt{hpc-arm64-research-beamfs}) targeting
\texttt{qemu-system-aarch64} on a Cortex-A57 core, with kernel
\texttt{linux-mainline} 7.0.1 (SRCREV
\texttt{3cb1fb7a56d2fd8011f5282bc170c0d23dc1f4b5}). The image
includes \texttt{fio}\,3.36, \texttt{trace-cmd}\,3.1.5, and
\texttt{perf}\,7.0.1 for benchmarking and tracing. The host
build is from \texttt{poky-hardened} 1.0 on a Gentoo Linux 2.18
machine.

\paragraph{Test image construction.}
The Yocto recipes for the test image are held in the
\texttt{roastercode/yocto-beamfs} repository (private, lockstep
with the public \texttt{roastercode/beamfs} kernel sources). A
public reproduction requires either reconstructing the recipes
from the on-disk format specification (normative,
\texttt{Documentation/format-v4.md}) and the kernel sources, and the kernel sources;
or requesting access to the private recipes for academic
reproduction. The maintainer commits to share the private recipes
on request to qualified academic researchers under a light NDA,
mirroring the policy applied to the companion RadFI methodology
paper. An independent rebuild from public artefacts alone is
feasible (the on-disk format is normatively specified and the
kernel sources are public at the cited tag), at the cost of
reconstructing the Yocto build environment from the standard
\texttt{poky-hardened} reference distribution.

\paragraph{Conformance fixture.}
The INLINE scheme conformance fixture is the canary block. Its
SHA-256 digests are normatively specified at
\texttt{Documentation/format-v4.md}\,\S\,11.5:
raw 4{,}096-byte disk block
\texttt{\seqsplit{fb8a3b9e2704ce3fc11a0d0a4139d36c916cb5e7230acde8d2fa00ace739a91c}},
3{,}824-byte user content gathered through the VFS alias
\texttt{/canary}
\texttt{\seqsplit{ced446d9bf5e6682a48e8782ce5ad33f575f08921451afaa127f26dc37515bab}}.
Cross-platform reproducibility is verified between an x86\_64 GCC
local build and an aarch64 cross-build, byte-identical.

\paragraph{Benchmark raw data.}
The raw \texttt{fio} JSON outputs (50 files, \(\sim\)346\,KiB
total) are committed under
\texttt{papers/2026-04-beamfs-v2/empirical/raw/}:
\texttt{b1-\{inode,ext4\}-r\{1..10\}.json} for B1,
\texttt{b2-\{inode,ext4\}-r\{1..10\}.json} for B2,
\texttt{b3-inline-r\{1..10\}.json} for B3. Re-run reproducibility
is at the distribution level (median p50 within a few percent),
not byte-identical, due to non-determinism in
\texttt{qemu-system-aarch64} time-keeping.

\paragraph{Figure generation.}
The matplotlib script
\texttt{papers/2026-04-beamfs-v2/figures/bench-plot.py}
regenerates Figs.~\ref{fig:b1-read}--\ref{fig:b3-inline} from the
raw JSON. The script requires Python 3.13 and matplotlib 3.10 or
later, and is invoked as \texttt{python3.13
papers/2026-04-beamfs-v2/figures/bench-plot.py}. The script reads
from \texttt{empirical/raw/} and writes to the same
\texttt{figures/} directory.

\paragraph{LOC audit.}
The 2{,}198 LOC count of \cref{tab:m2c-trace} is reproducible by
the awk pipeline of
\texttt{empirical/palier4-loc.md}, applied to the \texttt{*.c}
and \texttt{*.h} files at the repository root.

\paragraph{Companion paper artefacts.}
The companion paper RadFI v1~\cite{desbrieres2026radfi} is held
in the same repository at
\texttt{papers/2026-04-radfi-v1/paper.md}, built via
\texttt{pandoc} + \texttt{lualatex} per the
\texttt{Makefile} provided. RadFI's reference implementation is
held in \texttt{roastercode/radfi} (private, pending peer review
of the methodology paper).

\paragraph{License and distribution.}
Source code is under the GPL-2.0 license. The present technical
report is under CC-BY-4.0. Citation by tag and commit hash is
preferred over DOI for the implementation, as commit hashes are
strict identifiers of the audited state; DOI references for the
present report are added at Zenodo upload time.
