\section{Faithfulness Theorem}\label{sec:faithfulness}

% Override theorem numbering: explicit IV.x via the underlying definition counter
\renewcommand{\thedefinition}{IV.\arabic{definition}}
\setcounter{definition}{0}

\subsection{Statement}

\begin{theorem}[Faithfulness of RadFI as SEU emulator]\label{thm:faithfulness}
Let \(\varepsilon_{\text{RadFI}}\) be the perturbation operator of
\cref{def:perturbation}, satisfying invariants F1--F5
(\cref{ssec:invariants}). Let \(\varepsilon_{\text{SEE}}\) be the
canonical SEU operator of~\cite{desbrieres2026beamfsv1}, parameterized
by a cross-section \(\sigma\) and a flux \(\Phi\). Let \(X\) be the
random variable counting bit-flips per unit of bio payload bytes
traversed, under \(\varepsilon_{\text{RadFI}}\) with
\(\mathit{prob} = p_R\) and a uniformly distributed I/O workload, and
let \(Y\) be the corresponding random variable under
\(\varepsilon_{\text{SEE}}\). Then for every \(\delta > 0\), there
exists a calibration \(p_R(\sigma, \Phi)\) such that the total
variation distance between the distributions of \(X\) and \(Y\) is
bounded:
\[
  d_{\text{TV}}(X, Y) \leq \delta.
\]
\end{theorem}

\subsection{Discussion}

\paragraph{What the theorem establishes.}
RadFI, parameterized by \(p_R\), can emulate any SEU regime up to
total variation \(\delta\), where \(\delta\) shrinks as the I/O
workload duration grows (asymptotic indistinguishability). The proof
(\cref{app:proof}) is a concentration argument on bio interception
counts, exploiting F4 and F5.

\paragraph{What the theorem does not establish.}
Faithfulness is statistical, not physical. RadFI does not reproduce
the spatial correlation of multi-bit upsets within a memory row, nor
the temporal clustering of solar particle event bursts. Both are
observable in beam-time data and absent from RadFI by design. v2 of
this report will discuss extensions (per-row MBU clustering, Poisson
burst arrivals) that close part of this gap.

\paragraph{Composition with BEAMFS.}
\cref{thm:faithfulness} of the present report
(\(\varepsilon_{\text{RadFI}}\) faithful) composes
with~\cite[Theorem~IV.1]{desbrieres2026beamfsv1} (BEAMFS recovery
sound under \(\mathcal{E}_{\text{SEE}}\)) only if the family
\(\mathcal{E}\) used by the BEAMFS theorem contains the distribution
emulated by RadFI. The empirical falsification reported in
\cref{sec:empirical} demonstrates that the v1 \(\mathcal{E}\) did
not.
