\section{Scope and Limitations}\label{sec:limitations}

We adopt the same posture as~\cite{desbrieres2026beamfsv1}: the
limitations section is structural, not concessionary.

\paragraph{v1 covers.}
The mathematical formalization of \(\varepsilon\)
(\cref{sec:operator}), the faithfulness theorem
(\cref{sec:faithfulness} with proof in \cref{app:proof}), the
three-tier descent to a Linux kernel module (\cref{sec:m2c}), and
two empirical applications: falsification of BEAMFS v1 and
corroboration of BEAMFS v2 INLINE.

\paragraph{v1 does not cover.}

\begin{itemize}
\item \emph{Multi-flip per bio.} v0.1.x flips at most one bit per
  intercepted bio. A real burst event ionizing multiple cells along
  a single particle track is not modelled.
\item \emph{MBU spatial correlation.} Multi-bit upsets in physically
  adjacent cells are correlated through the particle's track
  geometry. RadFI's uniform sampling does not reproduce this
  correlation.
\item \emph{Beam-time calibration.} The faithfulness theorem
  (\cref{thm:faithfulness}) is a statistical claim; physical
  equivalence with accelerator-measured upset distributions is not
  established.
\item \emph{RDMA fast path.} RadFI hooks the bio layer; RDMA paths
  bypassing this layer are not intercepted.
\item \emph{Hook diagnostic on Linux 7.0.x.} The \texttt{hook\_blk}
  pre-handler observed on 2026-04-29 to register without firing
  under controlled conditions remains unexplained at v0.1.2.
  Diagnosis is deferred.
\item \emph{Verified compilation.} The kernel implementation is C;
  the gap from algorithm to executed binary is the standard
  unverified-compilation gap~\cite{klein2009sel4}.
\end{itemize}

\paragraph{Methodological limits.}
The author is the sole contributor; no peer review beyond the
public visibility of the BEAMFS repository has shaped this text.
The falsification of BEAMFS v1 is a self-falsification: the same
author wrote v1, RadFI, and the present retraction. We claim this
is a strength rather than a weakness --- a single author's
willingness to falsify their own theorem is a stronger Popperian
commitment than third-party falsification --- but we acknowledge
the absence of independent replication is a v2 priority.

\paragraph{Threats to validity.}
The principal threat is that the perturbation distribution emulated
by RadFI is not faithful to the SEU distribution observed in
deployed systems. \cref{thm:faithfulness} establishes statistical
indistinguishability under stated hypotheses, but the hypotheses
themselves (uniform sampling, single-bit primitive, no spatial
correlation) are simplifications. v2 will address each.
